Notes on generating initial models for mapping into {\tt MAESTRO}

### 2008-08-25 docs/initial_models/paper.tex
reflects what the code is currently doing

\item Compute $p_0$ using equation (\ref{HSE Discretization}), using $p_{0,r=0}$ as the initial condition.\MarginPar{We may change the location of the initial condition.}

@@

\item Copy the initial data from the dots directly into the circles.  For the squares, compute only $\rho$ and $X$ by using linear interpolation from the two nearest corresponding dots.\MarginPar{Maybe we should use quadratic interpolation?}

@@

Integrating the HSE discretization upward, when we encounter a change from coarse to fine, here is an equation to integrate up to the coarse-fine interface

>>>>

\item Compute $p_0$ using equation (\ref{HSE Discretization}), using the pressure at the top of the domain as the initial condition.  Note that we still integrate upwards from the bottom, but then offset the final pressure so the pressure at the top of the domain remains unchanged.

@@

\item Copy the initial data from the dots directly into the circles.  For the squares, compute only $\rho$ and $X$ by using linear interpolation from the two nearest corresponding dots.

@@

Integrating the HSE discretization upward, when we encounter a change from coarse to fine, here is an equation to integrate up to the coarse-fine interface ($l$ is the ``finer'' level, $l-1$ is the ``coarser'' level)
